---
title: "Interactive Map with Leaflet"
author: "MAK"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## Welcome to My Interactive Map!

This webpage was created to showcase the powerful mapping capabilities of R using the **Leaflet** package. Below, you will find an interactive map featuring custom markers and layers.

### About This Page

-   **Author**: MAK
-   **Creation Date**: `r Sys.Date()`

### Interactive Map

Explore the map below to see interactive features like zoom, pan, and custom markers.

```{r leaflet-map, message=FALSE, warning=FALSE}
# Create a leaflet map with custom markers
leaflet() %>%
  addTiles() %>%
  setView(lng = -122.4194, lat = 37.7749, zoom = 12) %>% # Centered on San Francisco
  addMarkers(lng = -122.4194, lat = 37.7749, popup = "Welcome to San Francisco!") %>%
  addMarkers(lng = -122.3984, lat = 37.7949, popup = "Ferry Building Marketplace") %>%
  addCircleMarkers(
    lng = -122.414, lat = 37.776,
    color = "red", radius = 10,
    popup = "A Highlighted Point"
  )
```

### Features of the Map

1.  **Interactive Controls**: Zoom and pan functionality.
2.  **Custom Markers**: Added markers with popups to display information.
3.  **Customization**: Highlighted points with circle markers and custom colors.

### Conclusion

This interactive map demonstrates how R Markdown and Leaflet can create visually engaging and functional web pages. Thank you for visiting!

------------------------------------------------------------------------
